---
title: "Novel research that will disrupt the industry"
author: "Mr scientist"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  github_document:
    toc: true
    toc_depth: 2
    pandoc_args: --webtex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, cache = T)
set.seed(1)
options(scipen = 999)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = c(
  "tidyverse", # best thing that happend to me
  "dbplyr", # dplyr syntax for DB query
  "data.table", # only way to run grouped calculations on tons of groups
  "pander", # pretty table rendering
  "gt" # event prettier tables
))
```

<br>

# Load data

```{r be sure to label chunks in an informative way, eval = F}
source("../passwords.R") # never post your passwords to Github again!
```

# Don't be afraid to add headers along the report  
<br>

## They'll all show up in the table of contents!  
<br>

# There's also plots and tables all around

```{r show a plot}
plot(mtcars$mpg, mtcars$cyl)
```

```{r show a table, results="asis"}
pandoc.table(head(mtcars[, 1:4]))
```

<br>

## gt tables

You can also include tables using the powerful `gt` package:

```{r}
as_raw_html(gt(head(mtcars[, 1:4])))
```


# Another cool option is doing code folding

<details><summary>SOME CODE</summary>
<p>

#### Like this!

```{r}
print("source: https://gist.github.com/joyrexus/16041f2426450e73f5df9391f7f7ae5f")
```

</p>
</details>

# Rendering Latex

You can render Latex on a github document by specifying in the YAML header:

```{r, eval=F}
output:
  github_document:
    pandoc_args: --webtex
```

Here's an example:

$$
X \sim \mathcal{N}(\mu,\sigma^2) \rightarrow f(x)= \frac{1}{\sigma \sqrt{2\pi}}e^{-\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^2}
$$