---
title: "Novel research that will disrupt the industry"
author: "Mr scientist"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, cache = T)
set.seed(1)
options(scipen = 999)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = c(
  "tidyverse", # best thing that happend to me
  "dbplyr", # dplyr syntax for DB query
  "data.table", # only way to run grouped calculations on tons of groups
  "pander", # pretty table rendering
  "gt" # even prittier table rendering
))
```

<br>

# Load data

```{r be sure to label chunks in an informative way, eval = F}
source("../passwords.R") # never post your passwords to Github again!
```

# Don't be afraid to add headers along the report  
<br>

## They'll all show up in the table of contents!  
<br>

# There's also plots and tables all around

```{r show a plot}
plot(mtcars$mpg, mtcars$cyl)
```

```{r show a table, results="asis"}
pandoc.table(head(mtcars[, 1:4]))
```

<br>

# Another cool option is doing code folding

<details><summary>SOME CODE</summary>
<p>

#### Like this!

```{r}
print("source: https://gist.github.com/joyrexus/16041f2426450e73f5df9391f7f7ae5f")
```

</p>
</details>

## gt tables in github_document

I've also found a nice workaround to incorporate tables from the **gt** package.

You can create the table object:

```{r create gt table}
# Define the start and end dates for the data range
start_date <- "2010-06-07"
end_date <- "2010-06-14"

# Create a gt table based on preprocessed
# `sp500` table data

a = sp500 %>%
  dplyr::filter(date >= start_date & date <= end_date) %>%
  dplyr::select(-adj_close) %>%
  gt() %>%
  tab_header(
    title = "S&P 500",
    subtitle = glue::glue("{start_date} to {end_date}")
  ) %>%
  fmt_date(
    columns = vars(date),
    date_style = 3
  ) %>%
  fmt_currency(
    columns = vars(open, high, low, close),
    currency = "USD"
  ) %>%
  fmt_number(
    columns = vars(volume),
    suffixing = TRUE
  ) 
```

And then at some point you can also view it using the `gt::gtsave` function:

```{r show gt table, hide=T}
gtsave(a, "try.png")
```

We next remove the resulting pic:

```{r remove gt table pic}
invisible(file.remove("try.png"))
```

It's a little shorter and easier to implement then inserting the resulting pic using standard markdown.